---
title: "Hyperbolic maximum finder"
output: html_notebook
---

So basically I have some spare time before bed to look at the problem. I think below is something that can work for the case you presented. The threshold can change depending on how finely resolved you want it to be. Your choice. Also, i added the delta part, because i am used to working in finite difference format (maybe that why i couldn't get my head around it earlier!!). 

Let me know if this is closer to what you aim to do or if you have found a better solution. 

Basically you have some equation (eg wave height) that get to a maximum value

$$ f(x) \rightarrow h_{max}$$
so we need to find:
$$y = f(x) $$
And then iteratively assign to $x$ back and forth with $y = f(x)$

$$ \begin{align} 
x_1 &= starting point (guess value) \\
y_1 &= f(x_1) \\
\text{where i = 1} \\ 
\text{next i = ....threshold} \\
x_i &= x_{i - 1} + \delta t \\
y_i &= f(x_i)
\end{align}

$$
# IMPLEMENTATION

```{r}

find_hmax <- function(func, starting_point = 0, dt = 0.1, threshold = 0.01){
# function find the maximum height of a hyperbolic function ()
# need function to calculate the value
# Zhou you can change the delta as you wish as well as the threshold
# Note the smaller the threshold the longer the time.
# I haven't tested the function well enough but it should work for 
# any tangent function 
x0 = starting_point
y0 = func(x0)
x1 = x0 + dt
y1 = func(x1)

iter = 0

while (abs(y1 - y0) > threshold) {
x0 = x1
y0 = func(x0)
x1 = x0 + dt
y1 = func(x1)
iter = iter + 1
cat("iteration :" , iter, "\n")
}

if(abs(y1 - y0) < threshold){
  cat("\nPoint where the difference between the two", deparse(substitute(func)), 
      "(x) is infinitesimally small\n")
  cat("difference between the two point", abs(y1 - y0), "\n")
  cat(deparse(substitute(func)), "(x) = ", y1)
}

invisible(y1) 
}
```


```{r}
# example 1
f = function(x) tanh(x)
plot(f(x), type = "o")
find_hmax(f, 0.0001)
hmax = find_hmax(f)
abline(h = hmax, lty = 2)
# example 2
f = function(x, y) x/(x + 1)
hmax = find_hmax(f, threshold = 0.008)
y = f(x)
plot(x, y)
par(new = TRUE)
abline(h = hmax, lty = 2)
```

